Exploring the Presidents Corpus

### 2019-11-07 Source/Paper 1 - Presidents Corpus Paper/PresidentsCorpus.tex
added abstract

\usepackage{arxiv}
\usepackage{float}
\usepackage{graphicx}

\begin{document}
\maketitle

\keywords{Mild Cognitive Impairment \and Alzheimer's Disease \and Machine Learning \and Diagnosis \and Natural Language Processing} 
\bigskip
\begin{abstract}
This paper looks at evidence of cognitive decline in three presidents speeches. Ronald Reagan, who would later go on to receive a diagnosis of Alzheimer's Disease and both George Herbert Walker Bush and Donald Trump who have no known diagnosis of dementia. This study used the methodology used by Berisha and Liss as a starting off point and offers some refinements in how the data was pre-processed, how the features were generated and how the analysis was conducted. We hypothesized that there would be features identified which would decline over time for RR, but not for our controls. We also hypothesised that a non-linear model would map decline more accurately than linear models. We collected data from the Question and Answer portions of the presidents press conferences and used Natural Language Processing to generate features for analysis. We found that there were a number of lexical features that significantly changed over time for RR but did not change for either GHWB or DJT. These features have a foundation in psychological literature and have been linked to cognitive decline in Alzheimer's Disease. Also, we found that non-linear models were able to more accurately map declines in RR's language over time. 
\end{abstract}

>>>>

\usepackage{arxiv}
\usepackage{float}
\usepackage{graphicx}
\begin{document}
\maketitle

\keywords{Mild Cognitive Impairment \and Alzheimer's Disease \and Machine Learning \and Diagnosis \and Natural Language Processing} 
\bigskip
\begin{abstract}
Several research efforts aimed at improving the early diagnosis of Alzheimer's Disease have focused on the longitudinal analysis of lexical features which have been implicated in the pre-clinical progression of this disease. We build on these studies and continue to refine a method for extracting and analysing language from transcripts. This method is based on a statistical evaluation of the most relevant features, as well as on the use of Generalised Additive Models instead of Linear Regression as a way to more adequately model the declines in language over time. We evaluate this method using the unscripted question and answer portions of news conferences from three U.S Presidents: Ronald Reagan (RR), who would later go on to receive a diagnosis of Alzheimer's Disease; George H. W. Bush (GB) and Donald Trump (DT), who have no known diagnosis of dementia. Our analysis uncovered several lexical features that did not change significantly for GB and DT, but presented significant changes for RR, including significant decreases in unique words and noun usage, and significant increases in pronouns (particularly personal pronouns), conjunctions and words which are related to social processes significantly increase over time. These findings are consistent with the psychological literature, which documents a link between these features and cognitive decline in Alzheimer's Disease. This work points the way to developing a comparatively non-invasive protocol that could be used in clinical settings that help to spot atypical declines in language use over time, potentially contributing to earlier, more accurate diagnoses of Alzheimer's Disease.

\end{abstract}
